With more than 1,5 billion active users, social networks are one of the most
popular Internet services.
The  problem is that social networks services of today are not scalable, 
having very high maintenance costs.
On the other hand, P2P services are robust, scalable and self-organized by nature, but have a
complete different architecture with new problems and unique requirements. 
 Therefore, this document focus on finding the existing problems in the
implementation of a P2P social networking service.
 We thoroughly investigate the requirements and features of social networks, along with the
challenges facing a P2P implementation. The main features discussed are (a)
the users login, (b) users posts, (c) users contacts list, (d) groups and organizations
among users, (e) privacy settings and (f) integration with other services and
applications.
After the analyzis of these features with their current solutions,
we discuss the problems that hinder the satisfaction of the system requirements, ending with the identification of today's main challenges.
Among the problems identified are (1) deficiencies in the
implementation of complex search, which do not allow real-time
feedback and need to improve the quality and accuracy of the results obtained,
(2) lack of proposals for enhanced security system for these systems,
especially related to selfish users control and encryption systems,
and (3) vulnerabilities in the entry mechanisms of the system and (4) management of
selfish users.\\


\textbf{Keywords:}  Social networks, p2p.
