%% TODO: introduction about the chapter
Next, we define the main assumptions and building blocks for our proposed
identification system, and formalize the notations used for its protocols.
After that, we describe the different parts of the system and how the
identification protocols will work.


\section{A pseudo-secure identification service}
\label{sec:pseudo-secure}
As shown in \cite{the_sybil_attack}, it is impossible to get a 100\% reliable
system over a DHT where malicious nodes are present. The goal of our approach
is to drastically reduce the probability of a malicious node being able to impersonate
another user using the identification system.

While the ability can always exist, it would be highly unlikely to happen
if we consider a very low probability, on the order of $10^{-14}$ for instance. The objective of 
the system is to obtain a probability of error lower than $10^{-14}$, while
maintaining an acceptable cost in system messages.

\section{Building blocks}
\label{sec:building_blocks}

For simplicity, we assume in the following that the underlying DHT is
Pastry~\cite{pastry}, as seen in section~\ref{sec:pastry}. We suppose that
every node in the DHT self-generates its own pair of public and privates keys
($X^{pub}$, $X^{priv}$) to be used with an asymmetrical encryption
algorithm.%~\cite{asymmetrical_encryption_algorithm}.

 The size of the keys used in the whole system is both fixed and large enough to make it computationally
unfeasible to decrypt any information without knowing the corresponding private
keys. We will also assume that a user is identified by the cryptographic proof of
his private key. SHA stands for the Secure Hash Algorithm One (SHA-1 - 160 bits hash). We also
assume that all communications among nodes are made using the TCP protocol, and
that all transmission errors are handled at the transport level.
A simple storage system is needed.
%% TODO:
%The \textit{trustsets} are in charge of the storage of the user keys that are
%used to identify a user in the system. The system needs a PUT(key,
%file) operation that stores the file in the closest trusted node based in the
%routing algorithm and a GET(key) operation that retrieves the stored file.


%%The identification system needs to use 


%% -- THIS IS NOT NECESSARY FOR THE IDENTIFICATION SYSTEM YET IT CAN BE USEFULL --
% Our final assumption is that the underlying operating system of every node which
%participates to the DHT is running the Network Time Protocol. Thus, we consider
%that every node has a good global time, wiuth a small deviation from the
%Coordinated Universal Time (UTC)

%\section{Securing  P2P networks}

%% TODO: Eval where to put this part about reputation systems

The protocols assumes a reputation system in the overlay structure with the following properties:
\begin{enumerate}
  \item Every node $X$ has an associated reputation value $R(X)$
  which represents the probability that $X$ is an honest node.
  \item $R(X)$ is computed using the recommendations emitted
  by nodes that have completed a transaction with $X$. Bad
  recommendations have a stronger effect on $R(X)$ than
  good ones because it should be more difficult for node to
  increase its reputation value than to decrease it.
  \item For every node $X$, $R(X)$ is highly available in the DHT.
\end{enumerate}

The reputation value $R(X)$, as seen in~\ref{sec:reputation_systems} is the probability that node $X$ will
be honest in the future. This reputation value is computed
according to a list of recommendations emitted by nodes that
have already carried out transactions with $X$.
After each transaction, a node emits a recommendation
about its peer. A node may lie: It may emit negative
recommendations about a peer that behaves correctly, or
positive recommendations about a malicious peer. Several nodes
may collude to increase or decrease the reputation value of
another node. These problems generate a deviation between
the computed reputation of the node and its real behavior. This deviation
depends on the function used to
compute the reputation value and on the percentage of malicious
nodes within the system.

To avoid nodes that lie about a reputation value, our system uses a reputation
system that computes the reputation of nodes concurrently on different nodes, as seen before in WTR~\ref{sec:wtr}.
They decide individually if that node is reputable or not, using a voting
scheme in cases of disagreement. On the whole, assuming that there is a small
percentage of malicious nodes in the network, the result avoids
false statements about reputation.

To maintain the same nomenclature seen in CORPS~\ref{sec:corps}, in all the following sections
we call a node $n_i \in TS$ a trusted node, even if there still remains a
probability that this node's actual reputation is smaller than the threshold
$\rho$.

\section{Notation}
% definition of a node and a service that is going to identify with it

Let $A$ be a node of the DHT, and $S = \{S_1, S_2, \cdots, S_n\}$ a set of $n$
nodes that cooperate to provide a service. Let $NameofS$ be the name of the service
$S$ provides. Every node that needs to use the service knows $NameofS$. $K_s =
SHA(NameofS)$ is the key that identifies $S$ in the DHT, and $S_{root}$ is the node
closest to $K_s$ in the DHT. It follows that $S = \{S_1, S_2, \cdots, S_n\}$ is
composed of node $S_{root}$ and of all the nodes in its leafset. Let $I$ be an
identification service such that $I = \{ I_1, I_2, \cdots, I_n\}$ is a group of
$n$ nodes belonging to the DHT. Let $L$ be the number of nodes in a
leafset: $card(S) = L + 1$.


% interaction between A, S & I, Figure and such

We suppose that the number of nodes that compose a service $S$ is fixed and does
not change over time. We also suppose that the same holds true for any
quasi-identification service $I$.
